---
title: "Week9-collab-doc"
format: html
---

Load Libraries
```{r}
library(tidyverse) #for data wrangling
library(lterdatasampler) #data
library(ggeffects) #for modeling
library(here) #for file pathing
```

Reading in data:
```{r}
data(pie_crab)
```

Visualizing data:
```{r}
ggplot(data = pie_crab, #using pie_crab data
       aes(x = latitude, #latitude on x axis
       y = size)) + #size on y axis
  geom_point(color = "blue1") + #scatterplot with blue points
  labs(x = "Latitude", #update axes labels
       y = "Size") +
  theme_minimal() #update theme
```
Writing model:
```{r}
crab_model <- lm(size ~ latitude, # formula(response ~ predictor)
                 data = pie_crab) # dataframe

par(mfrow = c(2, 2)) # display plots in 2x2 grid
plot(crab_model) # plot diagnostics
```
Run & interpret model
```{r}
summary(crab_model) #look at model
```
Summarize results

slope = 0.485
y-int = -3.62 ± 1.274

For each 1º increase in latitude, we expect crab size to increase by 0.485 ± 
0.034 mm.

Model Statistics: F(1,390) = 208.5,p < 0.001, alpha = 0.05, R^2^ = 0.35

general notes abt collab:
1. always save changes, commit/push!
2. comment code so ppl know what ur doing
3. TALK to collaborators!!!!
4. always pull before start working in code!!!!

